Multilevel regression models

### 2023-10-25 procesamiento/prod_analysis-full-sample.Rmd
update

stata('estimates use output/fullsample-ologit-homclass-respondent-macro')

>>>>

stata("")

clear all
eret list
estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(1)
estimates store model1
estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(2)
estimates store model2
estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(3)
estimates store model3
estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(4)
estimates store model4
estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(5)
estimates store model5
estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(6)
estimates store model6
estimates use 'C:\Users\jiturra\Documents\documentos-pcloud\rgroups-redist\output\fullsample-ologit-homclass-respondent-macro.est',  number(7)
estimates store model7

esttab model1 model2 model3 model4 model5 model6 model7, drop(logrgdpna 1.class3 2.class3 3.class3 female agenum edyears workst union 1.Q03pcm 2.Q03pcm 3.Q03pcm 4.Q03pcm )
